Exploring mathematical objects from custom-tailored mathematical universes

### 2020-06-30 paper-filmat.tex
Improve sentence (in response to review)

This property is where the language of toposes derives its usefulness for
mathematical practice from: In some cases, the easiest way to prove a result
(about objects of the standard topos) is
\begin{enumerate}
\item to observe that the claim is
equivalent to the Kripke--Joyal translation of a different (typically more
transparent) claim about objects of some problem-specific relevant topos and
then
\item to verify this different claim, reasoning internally to the topos.
\end{enumerate}

>>>>

The language of toposes derives its usefulness for mathematical practice from
this complexity reduction: In some cases, the easiest way to prove a result
(about objects of the standard topos) is
\begin{enumerate}
\item to observe that the claim is
equivalent to the Kripke--Joyal translation of a different (typically more
transparent) claim about objects of some problem-specific relevant topos and
then
\item to verify this different claim, reasoning internally to the topos.
\end{enumerate}
